Level-Set method on \texttt{p4est}

### 2015-01-01 paper/tex/applications.tex
added scaling figures for stefan, starting to work on that part

%!TEX root = draft.tex
\section{Application to Stefan Problems}

@@

@@

\begin{figure}[ht!]
\begin{center}
\includegraphics[width=.8\textwidth]{pictures/crystal_grid_low.png}
\end{center}
\end{figure}

>>>>

%!TEX root = draft.tex
\section{Application to Stefan Problems} \label{sec:application}

@@

\begin{figure}
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{figures/stefan_scaling_small.pdf}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{figures/stefan_scaling_large.pdf}}
\caption{Scalability of the Stefan problem for small (left) and large (right) octrees with roughly 7M and 105M grid points, respectively. As expected from the scalability analysis of the individual components, we observe excellent results, illustrating the potential of our solver.}
\label{fig:stefan_scaling}
\end{figure}

@@

\begin{figure}[ht!]
\begin{center}
\subfigure[]{\includegraphics[width=0.45\textwidth]{figures/stefan_grid.png}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{figures/stefan_grid_zoom.png}}
\caption{} \label{fig:stefan_grid}
\end{center}
\end{figure}

### 2015-01-01 paper/tex/introduction.tex
added interpolation results
added scaling figures for stefan, starting to work on that part

The rest of this article is organized as follows: In section \ref{sec:levelset method} we briefly review the sequential algorithms and discretization methods for the level-set equation on adaptive tree-based grids. These ideas are then extended in section \ref{sec:parallel algorithms} to parallel using a domain decomposition method. In section \ref{section::scaling results} we provide several examples that illustrate the scalability of our algorithms. Finally, we close by providing an important application of our algorithms in modeling the solidification process by solving a Stefan problem in \ref{section::applications}.

>>>>

The rest of this article is organized as follows: In section \ref{sec:levelset method} we briefly review the sequential algorithms and discretization methods for the level-set equation on adaptive tree-based grids. These ideas are then extended in section \ref{sec:parallel algorithms} to parallel using a domain decomposition method. In section \ref{sec:scaling} we provide several examples that illustrate the scalability of our algorithms. Finally, we close by providing an important application of our algorithms in modeling the solidification process by solving a Stefan problem in \ref{sec:application}.
